Fig3

### 2020-03-09 analysis/figure-3.Rmd
new figs

b11 <- makenewbargraph("hypothalamus", "female","eggs vs. chicks", 0, 2500) +  labs(subtitle = "females", x = NULL, y = " ") + 
  theme( axis.text = element_blank())
b21 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 2500)  + labs(x = NULL, y = " ") + 
  theme(axis.text = element_blank())
b31 <- makenewbargraph("gonad", "female", "eggs vs. chicks", 0, 2500) + labs(x = "eggs vs. chicks", y = " ")    + 
  theme(axis.text = element_blank())
b112131 <- plot_grid(b11,b21,b31, nrow = 3, rel_heights = c(1.1,1,1.1))

@@

c11 <- makenewbargraph("hypothalamus", "female", "lo vs. hi PRL   ", 0, 2500) +  labs(subtitle = "females", x = NULL, y = "hypothalamus DEGs") + 
  theme( axis.text.x = element_blank()) 
c21 <- makenewbargraph("pituitary", "female", "lo vs. hi PRL   ", 0, 2500)  + labs(x = NULL, y = "pituitary DEGs")+ 
  theme( axis.text.x = element_blank())
c31 <- makenewbargraph("gonad", "female", "lo vs. hi PRL   ", 0, 2500) + labs(x = "lo vs. hi PRL", y = "gonad DEGs")  + 
  theme(axis.text.x = element_blank()) 
c112131 <- plot_grid(c11,c21,c31, nrow = 3, rel_heights = c(1.1,1,1.1))

@@

hypothesisbars <-  plot_grid(c112131, c122232, b112131, b122232, nrow = 1, rel_widths = c(1.3, 1, 1.1, 1),
          labels = c("f", " ", "g", " "), label_size = 8)

>>>>

b11 <- makenewbargraph("hypothalamus", "female","eggs vs. chicks", 0, 2500) +  labs(subtitle = "females", x = NULL, y = "hypothalamus DEGs") + 
  theme( axis.text.x = element_blank())
b21 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 2500)  + labs(x = NULL, y = "hypothalamus DEGs") + 
  theme(axis.text.x = element_blank())
b31 <- makenewbargraph("gonad", "female", "eggs vs. chicks", 0, 2500) + labs(x = "eggs vs. chicks", y = "hypothalamus DEGs")    + 
  theme(axis.text.x = element_blank())
b112131 <- plot_grid(b11,b21,b31, nrow = 3, rel_heights = c(1.1,1,1.1))

@@

c11 <- makenewbargraph("hypothalamus", "female", "lo vs. hi PRL   ", 0, 2500) +  labs(subtitle = "females", x = NULL, y = " ") + 
  theme( axis.text = element_blank()) 
c21 <- makenewbargraph("pituitary", "female", "lo vs. hi PRL   ", 0, 2500)  + labs(x = NULL, y = " ")+ 
  theme( axis.text = element_blank())
c31 <- makenewbargraph("gonad", "female", "lo vs. hi PRL   ", 0, 2500) + labs(x = "lo vs. hi PRL", y = " ")  + 
  theme(axis.text = element_blank()) 
c112131 <- plot_grid(c11,c21,c31, nrow = 3, rel_heights = c(1.1,1,1.1))

@@

hypothesisbars <-  plot_grid(b112131, b122232, c112131, c122232, nrow = 1, rel_widths = c(1.3, 1, 1.1, 1),
          labels = c("f", " ", "g", " "), label_size = 8)
